Understanding LIME

### 2019-11-18 journals/02-understanding_lime/02-understanding_lime.Rmd
added implementation for feature_select

>>>>

```{r}
# Set up and implementation
x <- hamby224_test %>% 
  arrange(case) %>%
  select(rf_features) %>% 
  na.omit()
explainer <- lime:::lime.data.frame(x = hamby173and252_train %>%
                                      select(rf_features), 
                                    y = hamby173and252_train %>%
                                      select(samesource), 
                                    model = as_classifier(bulletr::rtrees))
label = TRUE
n_labels = NULL
n_features = 3
n_permutations = 5000
feature_select = 'auto'
dist_fun = "gower"
kernel_width = NULL
gower_pow = 1
o_type <- lime:::output_type(explainer)
if (is.null(kernel_width)) {
   kernel_width <- sqrt(ncol(x)) * 0.75
}
kernel <- lime:::exp_kernel(kernel_width)
case_perm <- lime:::permute_cases.data.frame(x,
                                             n_permutations,
                                             explainer$feature_distribution,
                                             explainer$bin_continuous,
                                             explainer$bin_cuts,
                                             explainer$use_density)
case_res <- lime:::predict_model(explainer$model, 
                                 explainer$preprocess(case_perm),
                                 type = o_type)
case_res <- lime:::set_labels(case_res, explainer$model)
case_ind <- split(seq_len(nrow(case_perm)), rep(seq_len(nrow(x)), each = n_permutations))
i <- case_ind[[1]]
if (dist_fun == "gower") {
  sim <- 1 - (gower_dist(case_perm[i[1], , drop = FALSE], 
    case_perm[i, , drop = FALSE]))^gower_pow
}
perms <- lime:::numerify(case_perm[i, ], 
                         explainer$feature_type, 
                         explainer$bin_continuous,
                         explainer$bin_cuts)

# Running the function
lime:::select_f_fs(x = as.matrix(perms), 
                   y = case_res[i, , drop = FALSE][[label]], 
                   weights = sim, 
                   n_features = n_features)
```

```{r}
# One implementation of the inside of select_f_fs

# Input values
x = as.matrix(perms)
y = case_res[i, , drop = FALSE][[label]]
weights = sim
n_features = n_features

# Creates a vector where to store the selected features
features <- c()

#for (i in seq_len(n_features)) {

# My code to run this loop
seq_len(n_features)
loopi <- 1

# Settings
max <- -1e+05
best <- 0

seq_len(ncol(x))

for (loopj in seq_len(ncol(x))) {

#if (loopj %in% features)
#  next

if (length(features) == 0) {

  x_fit = cbind(`(Intercept)` = rep(1, nrow(x)), x[, loopj, drop = FALSE])
  print(head(x_fit))

  fit <- glm.fit(x = x_fit, y = y, weights = weights, family = gaussian())

  r2 <- 1 - fit$deviance/fit$null.deviance
  print(r2)

  } else {

    x_fit = x[, c(features, loopj), drop = FALSE]
    print(head(x_fit))
    fit <- glmnet(x_fit,
                  y, weights = weights, alpha = 0, lambda = 0)

    r2 <- fit$dev.ratio
    print(r2)
  }

if (is.finite(r2) && r2 > max) {
  max <- r2
  best <- loopj
  print(max)
}

}

if (best == 0) {
             stop("Failed to select features with forward selection. Please choose another feature selector",
                 call. = FALSE)
}

features <- c(features, best)

#}

features
```
